The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
add mcgarigal

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection:
(1) the geographical range of a species, (2) the home range of an individual, the (3) habitat patches within the home range and (4) specific resources within a
habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of selection was insufficient for capturing landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a scale larger than their home range size. Moving past this hierarchical perspective, Mayor (2007) emphasized the importance of considering a broad continuum of scales to reveal scale-dependent selection and avoid the bias of predefined scales assumed to be associated with certain behaviors.

Then to Mayor 2009

<!-- And more recent? -->

Despite this, still not widely adopted McGarigal 2016

For
example, @Mayor_2007 showed caribou select for shallow snow at all scales 
and by using a continuum of scales, .

@@

Multilayer networks explicitly consider habitat selection and
sociality across scales. Animal social systems can be parsed by spatial
contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
The effect of resource phenology can be directly measured by differences in
habitat selection and sociality across temporal layers. Habitat selection can be
explicitly integrated using network layers defined by similarity of selection
coefficients between individuals. These explicit integrations of habitat
selection and sociality across social, spatial and temporal scales highlight the
potential for novel insights from multilayer networks.

>>>>

<!-- TODO: point to figure 1 -->
Habitat selection depends on the scale at which it is measured and a singular
scale is insufficient for generalizing across scales [@Mayor_2009]. Habitat
selection is measured using resource selection functions (RSFs), based on the
proportion of used and available resources for an animal [@Manly_1993;
@Boyce_1999]. Johnson (1980) identified four orders of habitat selection: (1)
the geographical range of a species, (2) the home range of an individual, the
(3) habitat patches within the home range and (4) specific resources within a
habitat patch. Kie et al. [-@Kie_2002] found that, independently, third order of
selection was insufficient for capturing landscape attributes selected for by
mule deer (*Odocoileus hemionus*), at a scale larger than their home range size.
Moving past this hierarchical perspective, Mayor (2007) emphasized the
importance of considering a broad continuum of scales to reveal scale-dependent
selection and avoid the bias of predefined scales assumed to be associated with
certain behaviors. Despite animals selecting for different landscape attributes
at different scales [@Mayor_2009], the use of multiscale analyses for habitat
selection is still critically lacking [@McGarigal_2016].

@@

Multilayer networks can be used to explicitly consider habitat selection and
sociality across scales. Animal social systems can be parsed by spatial
contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
The effect of resource phenology can be directly measured by differences in
habitat selection and sociality across temporal layers. Habitat selection can be
explicitly integrated using network layers defined by similarity of selection
coefficients between individuals. These explicit integrations of habitat
selection and sociality across social, spatial and temporal scales highlight the
potential for novel insights from multilayer networks.
